---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

### Step 1 Result

```{r head, include=TRUE}
library(classdata)
head(ames)
summary(ames)
```

-   Some of the variables in the data include Parcel ID(Categorical), Address(categorical), Style(categorical), Sale data(categorical), Sale price(numerical), LotArea(sf)(numerical),FinishedBsmtArea (sf)(numerical),Bedrooms(numerical),acres(numerical),YearBulit(categorical),AC(categorical), andFireplace(categorical)

### Step 2 Result

-   The main variable we're focusing on presently is Sale Price.

### Step 3 Result

```{r}


library(ggplot2)


ggplot(


  data=ames, 


  aes(x=log(get('Sale Price')))


)+ 


  geom_histogram(binwidth=1)+


  labs(x="Log-scale Sale Price")


```

-   Running the histogram outside of log scale reveals very large outliers. There are also some very low numbers. The total range is from 0 to 20 million \### Step 4 Result

-   Gwen's Results:

    ```{r}
    # This varible holds the log of sale price
    ames$LogSalePrice <- log(ames$`Sale Price`)

    # This is a box plot of neighborhood vs the log sale price 
    ggplot(ames, aes(x = Neighborhood, y = LogSalePrice)) +
      geom_boxplot(outlier.colour = "red") +
      labs(title = "Log Sale Price by Neighborhood", x = "Neighborhood", y = "Log(Sale Price)") +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 90, hjust = 1))


    ```

    ```{r}
    # Find the top and bottom 5 neighborhoods
    top_neighborhoods <- ames %>%
      group_by(Neighborhood) %>%
      summarise(MedianPrice = median(`Sale Price`, na.rm = TRUE)) %>%
      arrange(desc(MedianPrice)) %>%
      head(5)

    bottom_neighborhoods <- ames %>%
      group_by(Neighborhood) %>%
      summarise(MedianPrice = median(`Sale Price`, na.rm = TRUE)) %>%
      arrange(MedianPrice) %>%
      head(5)

    # Print the most and least expensive neighborhoods
    top_neighborhoods
    bottom_neighborhoods

    ```

    -   There is no range for the Neigborhood variable, since it is categorical. It appears that neighborhoods have an effect on Sale price. According to the box-plot, there are certain neighborhoods that have higher median sale prices. You would expect that nicer neighborhoods with luxury houses would have houses that are more expensive.

    -   Outliers can be seen throughout the box plot and there seem to be quite a few in high-priced neighborhoods. Many neighborhoods show high variability indicating that houses in the same area can sell at a wide range of prices.

-   Ben's Results:

```{r head, include=True}
library(ggplot2)

df_clean <- drop_na(ames)
ggplot(df_clean, aes(x=log(get('Sale Price')), y=Acres)) + 
  geom_point()

ggplot(ames, aes(x=log(get('Sale Price')), y=Acres)) + 
  geom_point()
```

-   Prices tend towards the same rough trends price wise, with larger lots tending to be more expensive, but not universally so. Relatively few legitimate outliers occur, with most lots tending to be roughy the same price and area. This is very reflective of the fact that most of the values fell into the same price range, with it being evident that they also all fall into the same rough acreage as well.

-   Zach's Results:

-   Adrian's Results:

```{r}
ames2 <- subset(ames, YearBuilt>0)
ggplot(
  ames2,
  aes(x=YearBuilt, y=log(get('Sale Price')))
)+
  geom_point()+
  labs(y='Price')
```

This plot does not reveal any explanations for irregularities. It seems that sales price remains fairly constant over years, with the lesser variety in older homes likely accounting for the smaller amount built from that time.
